### 2023-06-22 tex/semirings.tex
[ writing ] mostly C3 related work
[ writing ] move semiring definition out of prelims

In summary, the structure we have required of the set of usage annotations is
that they have addition (for $\otimes$-introduction and similar rules),
multiplication (for $\oc$-introduction), a $1$ (for a variable being used), a
$0$ (for a variable not being used), and an ordering (allowing for subsumption
of usage restrictions).
Together, these form a \emph{partially ordered semiring} (posemiring), the laws
of which are both supported by examples and necessary for the syntax to be well
behaved.
%\todo{Refer back to preliminaries for definition of posemiring}
For concreteness, I collect together the definition of the
$\{\gr0, \gr1, \gr\omega\}$ posemiring I have been using so far.

@@

\section{A usage-annotated calculus $\name$}\label{sec:lr}
\input{lr.tex}
\section{Bunched connectives}\label{sec:lnd}
\input{lnd.tex}
\section{Additions to and variations of \name{}}\label{sec:variant}
\input{rec.tex}
\section{Translation to and from existing systems}\label{sec:translation}
\input{trans.tex}

>>>>

In summary, the structure we have required of the set of usage annotations is
that they have addition (for $\otimes$-introduction and similar rules),
multiplication (for $\oc$-introduction), a $1$ (for a variable being used), a
$0$ (for a variable not being used), and an ordering (allowing for subsumption
of usage restrictions).
Together, these form a \emph{partially ordered semiring} (posemiring), the laws
of which are both supported by examples and necessary for the syntax to be well
behaved.

\begin{definition}
  A \emph{semiring} is a monoid in the multicategory of commutative monoids and
  multilinear maps.
  Unpacked, this means that we have a set $\mathscr R$ together with elements
  $0$ and $1$ and binary operators $+$ and $\cdot$ (with $\cdot$ usually written
  as juxtaposition) such that the following hold for all
  $x, y, z \in \mathscr R$.
  \begin{itemize}
    \item $0 + x = x$; $x + 0 = x$; $(x + y) + z = x + (y + z)$; $x + y = y + x$
    \item $1x = x$; $x1 = x$; $(xy)z = x(yz)$
    \item $0x = 0$; $x0 = 0$; $(x + y)z = xz + yz$; $x(y + z) = xy + xz$
  \end{itemize}
\end{definition}
\begin{definition}
  A \emph{posemiring} is a semiring in the category of partially ordered sets
  (posets).
  Unpacked, this means that we have a semiring (in the category of sets)
  $(\mathscr R, 0, +, 1, \cdot)$ such that $\mathscr R$ has a partial order
  (written $\leq$) and addition and multiplication are monotonic with respect
  to $\leq$ in both arguments.
\end{definition}

For concreteness, I collect together the definition of the
$\{\gr0, \gr1, \gr\omega\}$ posemiring I have been using so far.

@@

\section{A usage-annotated calculus $\name$}\label{sec:lr}
\input{lr.tex}
\section{Bunched connectives}\label{sec:lnd}
\input{lnd.tex}
\section{Additions to and variations of \name{}}\label{sec:variant}
\input{rec.tex}
\section{Representing existing linear and modal logics}\label{sec:translation}
\input{trans.tex}
